Monte Carlo and bootstrap for all parameters with tables

### 2024-09-13 Results/All3_tab_algo6_strat.Rmd
Cleaner strat files

\textbf{Basic bootstrap} is used.

@@

# Example: Algorithm 6 with basic bootstrap

@@

res2 <- MC_boot(n, B1, B2, fun_samp)

@@

```{r RS_algo6}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo6}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo6}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_algo6}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

\textbf{Stratified bootstrap} is used.

@@

# Example: Algorithm 6 with stratified bootstrap

@@

res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)

@@

```{r RS_algo6_strat}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo6_strat}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo6_strat}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_algo6_strat}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

### 2024-09-13 Results/All3_tab_algo7_strat.Rmd
Cleaner strat files

# Example: Algorithm 7 with basic bootstrap

@@

```{r RS_algo7}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo7}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo7}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_algo7}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

# Example: Algorithm 7 with stratified bootstrap

@@

```{r RS_algo7_strat}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo7_strat}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo7_strat}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r RB_algo7_strat}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

### 2024-09-13 Results/All3_tab_algo8_strat.Rmd
Cleaner strat files

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees, the ratio volume of trees / number of trees as well as for \textbf{other totals and ratios}) and variances of these estimators. The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances. We may also compare the coverage rates of each type of confidence interval.

In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.

@@

```{r}
fun_samp <- sampling_grid3
```

@@

res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)
# Just one circle to begin with

@@

```{r}
# Table for comparison
DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(round(rs_df, digits = 2), "%") )
```

```{r RS_algo8_strat}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Relative stability of variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications"), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo8_strat}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo8_strat}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r}
# Table for comparison
diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), "%") )
```

```{r RB_algo8_strat}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case"), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

>>>>

The goal of this document is to create a large number of Monte Carlo iterations to produce estimators (for the number of trees, the volume of trees, the ratio volume of trees / number of trees as well as for \textbf{other totals and ratios}) and variances of these estimators. The same elements, along with confidence intervals, are also computed for each bootstrap series derived from a smaller number of Monte Carlo iterations. By comparing the two results, we may ensure the validity of the bootstrap strategy to find the estimation of the variances. We may also compare the characteristics of each type of confidence interval.

In this document, \textbf{sampling through a grid} is used to create a sample, more precisely \textbf{Algorithm 8}, and \textbf{three concentric circles} are used to compute local variables.

@@

```{r}
# The adequate function and its name
k <- 4 # Algorithm 8
fun_samp <- fun_tech[k][[1]]
name_samp <- samp_tech[k]
```

@@

res2 <- MC_boot(n, B1, B2, fun_samp, strat = TRUE)

@@

```{r}
# Table for comparison
DF_rs <- data.frame(`Parameter of interest` = PARAM_names, `Relative stability` = paste0(format(round(rs_df, digits = 2), nsmall = 2), "%") )
```

```{r RS_algo8_strat}
tab_rs <- DF_rs %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\hline"), caption = paste0("Approximation of Relative Stability of bootstrap variance by using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp), col.names = gsub("[.]", " ", names(DF_rs))) %>% # \\hline \\addlinespace
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", full_width = FALSE, 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```

@@

```{r CI_tot_algo8_strat}
tab_ci1 <- df_total1 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (totals)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0, 16), hline_after = T) %>% 
  row_spec(c(16), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r CI_ratio_algo8_strat}
tab_ci2 <- df_total2 %>%
  kable("latex", booktabs = FALSE, align = "llcccc", caption = paste0("Characteristics of confidence intervals when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications with ", name_samp, " (ratios)")) %>%
  kable_styling(latex_options = "hold_position") %>%
  row_spec(0, bold = TRUE) %>%
  row_spec(c(0), hline_after = T) %>% 
  # row_spec(c(16,32), hline_after = T) %>% 
  collapse_rows(columns = 1, valign = "middle")
```

@@

```{r}
# Table for comparison
diff_var <- data.frame(`Parameter of interest` = PARAM_names, `Monte Carlo Relative Bias` = paste0(format(round(mapply(function(x,y){unlist(100*(y-x)/x)}, res1$Variances, VAR_df), digits = 2), nsmall = 2), "%") )
```

```{r RB_algo8_strat}
tab_var <- diff_var %>%
  kable("latex", booktabs = FALSE, align = "lc", linesep = c("", "", "",
  "\\addlinespace"), caption = paste0("Approximation of Relative Bias of bootstrap variance when using ", B1, " Monte Carlo iterations and ", B2, " bootstrap replications in one case and ", B0, " Monte Carlo iterations in the other case with ", name_samp), col.names = gsub("[.]", " ", names(diff_var))) %>% # \\hline
  kable_styling(latex_options = c("striped", "hold_position")) %>% # bootstrap_options = "striped", 
  row_spec(0, bold = TRUE) %>% # , hline_after = TRUE
  row_spec(c(0, 4, 8), hline_after = T) %>% 
  collapse_rows(columns = 1, latex_hline = "major")
```
